---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sola

<!-- badges: start -->
<!-- badges: end -->

The goal of `sola` is to provide tools for solar resource assessment and utilization. This package implements the function of calculating solar radiation based on sunshine hours, latitude, and other related parameters. Compared with other existing packages, the main advantage of `sola` is the use of vectorization operations, allowing for efficient calculation of large datasets. The package is continuously updated to include more functions relevant to solar energy resource assessment.

## Installation

You can install the development version of sola from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("renliang1996/sola")
```

## Example

Here is a simple example of calculating solar radiation:

```{r example}
library(sola)

# Calculate solar radiation for March 15, 2023, at latitude 35 with 8 hours of sunshine
sol_rad(lat = 35.0, date = as.Date("2023-03-15"), ssd = 8)
```

### Vectorization calculation

To address the limitation of certain packages that can only input a single value, we can input a vector for computation:

```{r vector}
latitudes <- c(35, -15, 50)
dates <- as.Date(c("2023-03-15", "2024-06-21", "2023-11-01"))
sunshine_hours <- c(8, 10, 6)

sol_rad(lat = latitudes, date = dates, ssd = sunshine_hours)
```

### Performance Testing with Large Datasets

The following example demonstrates how `sola` can handle a dataset with 10,000 records efficiently:

```{r Large Datasets}
set.seed(123)
test_lat <- runif(10000, -90, 90)
test_date <- as.Date("2023-01-01") + sample(1:365, 10000, replace = TRUE)
test_ssd <- runif(10000, 0, 24)

system.time({
  results <- sol_rad(lat = test_lat, date = test_date, ssd = test_ssd)
})
head(results)
```

